R functional programming approach for truncated and shifted and for shifted

### 2016-09-21 docs/shift+trunc-article/article-shift+trunc.Rmd
article shift+trunc in pdf + metadescription

---
title: "R functional programming approach for truncated and shifted and for shifted and truncated probability distribution functions"
output: html_document
---

>>>>

---
title: R functional programming approach for truncated and shifted and for shifted
  and truncated probability distribution functions
output:
  pdf_document: default
  html_document:
    highlight: null
    theme: null
---
